Efficient Constructions of Prefer-Max Sequences and of Infinite de Bruijn Sequences

### 2017-01-08 paper.tex
...

The observation made in the last theorem directed us to examine the reverse of the prefer-max sequence. Specifically, the structure identified in Theorem~\ref{thm:onion} means that, if we manage to construct the sequence backwards, we do not have to specify $k$ ahead of time. Instead, we can add symbols forever while $k$ grows in layers: we first write $0^n$, then a word whose substrings of length $n$ are $\{0,1\}^n$, then extend with other words in $\{0,1,2\}^n$, and so on.

The second contribution of this work is then an efficient construction of this reversed sequence. This is formulated in Algorithm~\ref{inf-construction}. We say that this construction is efficient because each step can be computed in $O(n^2)$ operations by enumerating all the $n$ rotations of $\sigma w$ and comparing them lexicographically (reading each word from right to left).

@@

\begin{repeatedtheorem}{thm:onion}[Onion]
	{The last $(k-1)^n+1$ symbols of the $(k,n)$-prefer-max sequence form the $(k-1,n)$-prefer-max sequence.}
\end{repeatedtheorem}
\begin{proof}
	Denote the symbols of the $(n-k$)-prefer-max sequence by
	$s_1,s_2,\dots,s_{k^n+1}$ and let, for notational convenience, $s_i=0$ for all
	$i<1$.  For each $i\geq 1$ let $w_i=s_{i-n+1}\cdots s_i$ be the ``sliding window''
	observed at the $i$th symbol of the sequence. 
	The proof goes by showing that $\{w_1,\dots,w_{k^n-(k-1)^n}\} = \{0,\dots,k-1\}^n \setminus \{0,\dots,k-2\}^n$.

>>>>

The observation made in the last theorem directed us to examine the reverse of the prefer-max sequence. Specifically, the structure identified in Theorem~\ref{thm:onion} means that, if we manage to construct the sequence backwards, we do not have to specify $k$ ahead of time. Instead, we can add symbols forever while $k$ grows in layers: we first write $0^n$, then a word whose substrings of length $n$ are $\{0,1\}^n$, then extend with other words in $\{0,1,2\}^n$, and so on.
1
The second contribution of this work is then an efficient construction of this reversed sequence. This is formulated in Algorithm~\ref{inf-construction}. We say that this construction is efficient because each step can be computed in $O(n^2)$ operations by enumerating all the $n$ rotations of $\sigma w$ and comparing them lexicographically (reading each word from right to left).

@@

\begin{repeatedtheorem}{thm:onion}[Onion]
	{The last $(k-1)^n$ symbols of the $(k,n)$-prefer-max sequence form the $(k-1,n)$-prefer-max sequence.}
\end{repeatedtheorem}
\begin{proof}
	Denote the symbols of the $(n,k$)-prefer-max sequence by
	$s_1,s_2,\dots,s_{k^n+1}$ and let, for notational convenience, $s_i=0$ for all
	$i<1$.  For each $i\geq 1$ let $w_i=s_{i-n+1}\cdots s_i$ be the ``sliding window''
	observed at the $i$th symbol of the sequence. 
	The proof goes by showing that $\{w_1,\dots,w_{k^n-(k-1)^n}\} = \{0,\dots,k-1\}^n \setminus \{0,\dots,k-2\}^n$.
